---
title: "SpatDiv"
subtitle: "Spatially Explicit Measures of Diversity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SpatDiv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a preliminary version of a package designed to measure spatially-explicit diversity.

# Getting started

Install the package for _R_ from Github.

```{r install, eval=FALSE}
library("remotes")
remotes::install_github("EricMarcon/SpatDiv")
```


# Demo

Create a random, spatialized community with 100 individuals of 10 species.

```{r rSpCommunity, message=FALSE}
library("SpatDiv")
rSpCommunity(n=1, size=100, S=10) -> spCommunity
autoplot(spCommunity, which.marks = "PointType")
```

Plot a rank-abundance curve.

```{r Whittaker}
autoplot(as.AbdVector(spCommunity))
```

## Diversity accumulation

### With respect to the number of indiduals

Compute the Diversity Accumulation Curve for 1 to 50 neighbors for orders 0, 1 and 2, with the theoretical, null-model curve.
Plot it for Shannon diversity.

```{r plotDivAccum, fig.width=6}
divAccum <- DivAccum(spCommunity, n.seq=1:50, q.seq=0:2, H0="Multinomial", NumberOfSimulations=1000)
autoplot(divAccum, q = 1)
```

Compute and plot the mixing index of any order.
Save the local values for future use.

```{r Mixing, fig.width=6}
mixing <- Mixing(spCommunity, n.seq=1:50, q.seq=0:2, H0="Multinomial", NumberOfSimulations=1000, Individual=TRUE)
autoplot(mixing, q = 1)
```

### With respect to distance

The same accumulation cuves can be computed by increasing the sample area around each point.
The argument \code{r.seq} contains the vector of radii of those circular plots.

```{r plotDivAccum2, fig.width=6, eval=FALSE}
divAccum <- DivAccum(spCommunity, r.seq = seq(0, .5, by=.1), q.seq=0:2, spCorrection = "Extrapolation", H0="Binomial")
autoplot(divAccum, q = 1)
```


### Null hypotheses

The actual accumulation curves of diversity and mixing index can be compared to null models with their confidence intervals.
Values of the argument \code{H0} can be:

- "None": No null model is run.
- "Multinomial": The accumulation follows a multinomial sampling, with respect to the number of individuals only. The theoretical value and confidence envelope are calculated by the _entropart_ package.
- "Binomial": The individuals are relocated in the window uniformly and independently.
- "RandomLocation": The individuals are relocated accross their actual locations.

The multinomial null hypothesis is by far faster to compute than the others because it does not require point pattern simulations.


## Map

Map the local diversity accumulation or mixing index, for example the species accumulation in 10 points (9 neighbors and the central point).

```{r MapPlot}
par(mar=c(0,0,0,0))
MapPlot(mixing, Order = 0, NeighborHood = 10)
```
