---
title: "Random Spatial Communities"
output: rmarkdown::html_vignette
bibliography: ../../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{Random Spatial Communities}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

**SpatDiv** allows drawing random, spatialized communities as a whole, or species by species for more control.

# Drawing random communities

The function `rSpCommunity()` draws a community (which is a weighted, marked, planar point pattern, i.e. a `wmppp` object defined in package **dbmss**) or a list of communities (an `SpCommunities` object) if argument `n`, the number of communities, is greater than 1.

```{r DefaultSpCommunity, eval=FALSE}
library("SpatDiv")
spCommunity <- rSpCommunity(1, size=30, S=5)
autoplot(spCommunity)
```

The random community obtained is made of 30 individuals in 5 species.
All arguments are set by default:

- The species distribution of abundances is lognormal.
- The spatial window is a square of side 1.
- The spatial distribution of each species is multiniomial (i.e. point locations are independent, but their number is fixed).
- The species point patterns are independent.
- The size of all individuals is 1.


# Drawing species separately

The function `rSpSpecies()` draws a single species spatial pattern, which is a a `wmppp` object.


```{r DefaultSpSpecies, eval=FALSE}
spSpecies <- rSpSpecies(50, Spatial = "Thomas")
autoplot(spSpecies)
```

The point pattern of a a species is aggregated.
It follows a Thomas point process with default arguments.


# Combining point patterns

Spatial communities stored in `wmppp` and `SpCommunities` objects can be superimposed by the `spatstat.geom::superimpose()`.

```{r}
library("tidyverse")
library("spatstat")
superimpose(spCommunity, spSpecies) %>% 
  autoplot()
```


# References
