---
title: "Random Spatial Communities"
output: rmarkdown::html_vignette
bibliography: ../../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{Random Spatial Communities}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r global_options, include=FALSE}
# Installation of packages if necessary
InstallPackages <- function(Packages) {
  InstallPackage <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {
      install.packages(Package, repos="https://cran.rstudio.com/")
    }
  }
  invisible(sapply(Packages, InstallPackage))
}
InstallPackages(c("magrittr", "spatstat", "dbmss", "SpatDiv"))
library("magrittr")
# knitr options
knitr::opts_chunk$set(
  cache =   TRUE,  # Cache chunk results
  echo =    TRUE,  # Show R chunks
  warning = FALSE, # Hide warnings
  message = FALSE, # Hide warnings
  fig.align='center', out.width='80%', fig.dim=c(7, 5),
  # Code chunk format
  tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=80)
  )
# Random seed
set.seed(97310)
```

**SpatDiv** allows drawing random, spatialized communities as a whole, or species by species for more control.


# Drawing random communities

The function `rSpCommunity()` draws a community (which is a weighted, marked, planar point pattern, i.e. a `wmppp` object defined in package **dbmss**) or a list of communities (an `SpCommunities` object) if argument `n`, the number of communities, is greater than 1.

```{r DefaultSpCommunity, message=FALSE}
library("SpatDiv")
spCommunity <- rSpCommunity(1, size=30, S=5)
autoplot(spCommunity)
```

The random community obtained is made of 30 individuals in 5 species.
All arguments are set by default:

- The species distribution of abundances is lognormal.
- The spatial window is a square of side 1.
- The spatial distribution of each species is multiniomial (i.e. point locations are independent, but their number is fixed).
- The species point patterns are independent.
- The size of all individuals is 1.


# Drawing species separately

The function `rSpSpecies()` draws a single species spatial pattern, which is a a `wmppp` object.


```{r DefaultSpSpecies}
spSpecies <- rSpSpecies(50, Spatial = "Thomas")
autoplot(spSpecies)
```

The point pattern of a a species is aggregated.
It follows a Thomas point process with default arguments.

Available point processes are:

- `Binomial`: points are draw independently like in a homogenous Poisson process but their number is forced to `n`.
- `Thomas`: points are clustered around centers whose density is `kappa`.
`mu` is the average number of points in each cluster.
`scale` is the standard deviation of the random displacement of points from the cluster centers.


# Combining point patterns

Spatial communities stored in `wmppp` and `SpCommunities` objects can be superimposed by the `superimpose()` function from package **dbmss**.

```{r superimpose, message=FALSE}
library("dbmss")
superimpose(spSpecies, spCommunity)  %>% 
  autoplot()
```


# References
