---
title: "Introduction to SpatDiv"
author:
- name: Eric Marcon
  affiliation: AgroParisTech, UMR EcoFoG
  email: eric.marcon@ecofog.gf
package: SpatDiv
output:
  BiocStyle::html_document
abstract: |
  Introduction to the package.
vignette: |
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Getting started

Install the `r Githubpkg("EricMarcon/SpatDiv")` package for _R_ from Github.

```{r install, eval=FALSE}
library("devtools")
devtools::install_gitub("EricMarcon/SpatDiv")
```


# Demo

Create a random, spatialized community with 100 individuals of 10 species.

```{r rSpCommunity}
library("SpatDiv")
rSpCommunity(n=1, size=100, S=10) -> spCommunity
plot(spCommunity, which.marks = "PointType")
```

Plot a rank-abundance curve.

```{r Whittaker}
plot(as.AbdVector(spCommunity))
```

## Diversity accumulation

### With respect to the number of indiduals

Compute the Diversity Accumulation Curve for 1 to 50 neighbors for orders 0, 1 and 2, with the theoretical, null-model curve.
Plot it for Shannon diversity.

```{r plotDivAccum}
divAccum <- DivAccum(spCommunity, n.seq = 1:50, q.seq=0:2, H0="Multinomial")
plot(divAccum, q = 1)
```

Compute and plot the mixing index of any order.
Save the local values for future use.

```{r Mixing}
mixing <- Mixing(spCommunity, n.seq = 1:50, q.seq=0:2, H0="Multinomial", Individual = TRUE)
plot(mixing, q = 1)
```
### With respect to distance

The same accumulation cuves can be computed by increasing the sample area around each point.
The argument \code{r.seq} contains the vector of radii of those circular plots.


### Null hypotheses

The actual accumulation curves of diversity and mixing index can be compared to null models with their confidence intervals.
Values of the argument \code{H0} can be:

- "None": No null model is run.

- "Multinomial": The accumulation follows a multinomial sampling, with respect to the number of individuals only. The theoretical value and confidence envelope are calculated by the _iNEXT_ package.

- "Binomial": The individuals are relocated in the window uniformly and independently.

- "RandomLocation": The individuals are relocated accross their actual locations.

The multinomial null hypothesis is by far faster to compute than the others because it does not require point pattern simulations.


## Map

Map the local diversity accumulation or mixing index, for example the species accumulation in 10 points (9 neighbors and the central point).

```{r MapPlot}
MapPlot(mixing, Order = 0, NeighborHood = 10)
```
